Energy and exergy analysis of a cruise ship

### 2018-05-08 Manuscript/Manuscript.tex
Update

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
%% Tthe amsmath package provides the "align" environment for nicer equation formatting
\usepackage{amsmath}
%% The package tabls helps in having nicer tables with higher spaces
\usepackage{tabls}
%% The package multirow allows merging together multiple cells vertifcally
\usepackage{multirow}
%% 
\usepackage{subcaption}

@@

For both auxiliary and main engines, part of the relevant internal variables are not measured (particularly with relation to the bypass valves) and this required to determine them based on modeling the heat and mass balance of the engine. In particular, the following equations are used:
\begin{itemize}
	\item Mass balance on the split after the compressor, with one flow going to the engine inlet valves and the other flow going to the bypass valve. 
	\begin{equation}
	\dot{m}_{air,comp} = \dot{m}_{air,cyl} + \dot{m}_{air,bypass} \\
	\end{equation}
	\item Mass balance on the mixer before the turbine, with one flow coming from the engine exhaust valves and the other flow coming from the bypass valve
	\begin{equation}
	\dot{m}_{eg,turb} = \dot{m}_{eg,cyl} + \dot{m}_{air,bypass} \\
	\end{equation}
	\item Mass balance in the engine cylinder:
	\begin{equation}
	\dot{m}_{eg,cyl} = \dot{m}_{air,cyl} + \dot{m}_{fuel,cyl} \\
	\end{equation}
	\item Energy balance on the turbocharger: the power generated by the turbine must be equal to the power absorbed by the compressor
	\begin{equation}
	\dot{m}_{air,comp} \Delta h_{comp} = \dot{m}_{eg,turb} c_{p,eg} (T_{turb,in} - T_{turb,out}) \eta_{mech}
	\end{equation}
	\item Energy balance on the mixer between the air flow after the bypass valve and the exhaust gas flow after the exhaust valve
	\begin{equation}
	\dot{m}_{air,bypass} c_{p,air} (T_{comp,out} - T_0) + \dot{m}_{eg,cyl} c_{p,eg}  (T_{cyl,out} - T_0) = \dot{m}_{eg,turb} c_{p,eg} (T_{turb,in} - T_0)
	\end{equation}
\end{itemize}

The energy balance over the whole engine is presented in Equation \ref{eqn:engineEnergyBalance}.
\begin{equation}
\dot{m}_{fuel} (LHV_{fuel} + c_{p,fuel} (T_{fuel,in} - T_0)) + \dot{m}_{air} c_{p,air} (T_{air,comp,in} - T_0) = \dot{W}_{mech} + \dot{m}_{eg} c_{p,eg} (T_{eg,TC,out} - T_0) + \dot{Q}_{cooling} 
\end{equation} \label{eqn:engineEnergyBalance}
With: 
\begin{equation}
\dot{Q}_{cooling} = \dot{Q}_{CAC,HT} + \dot{Q}_{CAC,LT} + \dot{Q}_{JWC} + \dot{Q}_{LOC}
\end{equation} \label{eqn:engineCoolingBalance}
The value of $\dot{Q}_{cooling}$ is determined based on the balance in Equation \ref{eqn:engineEnergyBalance}. The share between the four contributions in Equation \ref{eqn:engineCoolingBalance} is calculated based on the data for the heat loss to the HT and LT systems presented in the engines project guides as functions of the engine load. The values are interpolated based on a 2$^nd$ degree polynomial and scaled to respect the energy balance. In absence of more accurate data, it is then assumed that the contributions of $\dot{Q}_{JWC}$ and $\dot{Q}_{LOC}$ are equal for all loads. CHANGE VALUES IN THE TABLE

\begin{table}
	\small
	\centering
	\begin{tabular}{lcrrrr}
		\hline
		Energy flow & type & 30\% & 50\% & 70\% & 90\% \\
		\hline
		Power output & Mech &  1767 & 2946 & 4118 & 5293 \\	
		Exhaust gas (after turbine) & Heat & 1672 & 2566 & 3227 & 3938 \\
		CAC-LT & Heat & 104 & 152 & 279 & 454 \\
		CAC-HT & Heat & 2 & 337  & 569 & 843  \\
		JWC & Heat & 381 & 249 & 278 & 318 \\
		LOC & Heat & 682 & 721 & 699 & 725  \\
		\hline
	\end{tabular}
	\caption{Main engines, energy flows at different engine loads}
	\label{tab:ME_flows}
\end{table}

		Exhaust gas (after turbine) & Heat & 808 & 1144 & 1456 & 1753 \\
		CAC-LT & Heat & 5 & 91 & 139 & 216 \\
		CAC-HT & Heat & 0 & 5 & 89 & 257  \\
		JWC & Heat & 176 & 314 & 396 & 467 \\ 
		LOC & Heat & 405 & 448 & 499 & 587  \\
		\hline
	\end{tabular}
	\caption{Auxiliary engines, energy flows at different engine loads}
	\label{tab:AE_flows}
\end{table}

@@

All values not directly measured in the cooling systems were calculated based on mass and energy balances.

@@

\subsection{Estimation of the electric power demand} \label{sec:met:electric}

@@

\subsection{Estimation of the heat demand} \label{sec:met:heat}

@@

\subsection{Determination of typical operational days}

@@

Figures \ref{fig:TseaTairTIME} and \ref{fig:TseaTairDIST} represent the time evolution and the distribution over the year of the ambient air and sea water temperature. The relatively low temperatures that are experienced by the case study ship during its operations rises expectations for a high space heating demand and to a relatively low for summer HVAC electric power demand. On the other hand, the fact that, in summer, air temperatures reach up to 26 degrees Celsius justify the existence of an HVAC unit that can also operate in cooling mode.

@@

Figure \ref{fig:vship_hist} represents the distribution of the ship speed. The ship operates almost for the entire year according to a fix schedule, while there are a couple of periods (particularly during the summer months) when the ship operates at higher speed. The relatively large amount of time the ship spends in port can also be seen in Figure \ref{fig:opMode_pie}. This suggests that, in spite of the high installed power for propulsion, the energy demand for this category is expected to be relatively low.

Figures \ref{fig:loadME_hist} and \ref{fig:loadME_hist} show the frequency of the load at which each of the engines (main and auxiliary engines, respectively) is operated.

@@

Here we can see the typical example (note: the day was not selected as "typical", but simply randomly) of the energy demand during a winter and a summer day (Figures \ref{fig:Demand_vs_time_W} and \ref{fig:Demand_vs_time_S}). It can be seen clearly how, as expected, the heating demand in winter is much higher than in summer [2800-4500 kW vs 1100-2900 kW], as a consequence of the reduce need for compartment heating. On the other hand, the electric power demand behaves inversely, ranging around 1900 kW during the reference winter day (peaks are connected to the use of thrusters in port for maneuvering) and around 2300 kW during the reference summer day, where the difference is mostly associated to the demand of the HVAC compressors.

@@

From Figure \ref{fig:Pie_EnergyDemand} it can be noted that nearly 50\% of the total energy demand is related to ship propulsion, while the remaining portion is approximately equally split between electric energy and heat demand.

Within the electric energy demand, the HVAC systems only represent a minor contribution (XX\%), as it is only present for a few months during summer, and at rather low power demand. This is not surprising, since it can be observed that (see Figure \ref{fig:TseaTairDIST}) the air is always below 27$^o$C, and rarely above 17$^o$C. Also the thrusters, although they represent a rather high instantaneous demand, they are only used for a very short time and, hence, their total contribution to the ship energy demand is limited to XX\%. As a consequence, most of the electric energy demand should be allocated to other consumers, and efforts should be directed towards providing additional measurements of how different users contribute to the total electric power demand.

Looking at Figure \ref{fig:Pie_HeatGeneration} it is possible to appreciate the amount of heat that is recovered from on board available waste heat (cooling water and exhaust gas). It can be observed that  of heat recovered from the HT cooling systems represents approximately one quarter of the total heat supply. Figure \ref{fig:TimeSeries_HeatGeneration} shows how the contribution of the HRSG and the HTHR is substantially constant throughout the year, while the auxiliary boilers are used to cover the peaks and the winter increased baseload.

@@

Regarding the heat demand onboard, it can be seen that the HVAC re-heater represents the largest contributor (XX\%) followed by the hot water heater (XX\%). The large contribution of the HVAC reheater can be explained by the former being important for long times and in relation to the low ambient temperatures encountered by the case study vessel during operation. The relatively large contribution of the hot water heater can instead be related to the fact that these systems are rather important consumers and are necessary during the whole ship operations (i.e. also during the summer months).

@@

It can be observed that there are large irreversibilities concentrated in some specific parts of the system that show potential for improvement. This is particularly the case of the LT/HT merging valves, where exergy is destroyed in the mixing process. Another substantial source of exergy destruction is the steam heater in the HTHR system, where heat at medium pressure (6 bar) is used to heat up water at 90$^o$C. The analysis of exergy destruction also points out the HVAC reheater as a potential source of improvement, based on the use of relatively high-temperature water for heating up air to around 30$^o$C and on the large energy demand of the component. Other important exergy destruction sources can be located in the engines, as expected, but the improvement of engine processes and technology goes beyond the scope of this work.

From the point of view of the exergy losses, it appears that the largest exergy losses are located in the exhaust gas. It should be noted that, even though a large part of this exergy cannot be recovered given the limitations on the exhaust gas outlet temperature to avoid the condensation of sulphuric acid, there is still a significant potential to be harvested if all the available exergy in the exhaust gas was recovered. This potential is further increased by the exergy destroyed in the process of dumping steam when it is produced in excess during summer. The exergy lost in the sea water coolers is much lower, highlighting the fact that the potential for improving the efficiency of the system is located in other parts of the cooling systems.

@@

OTHER?

@@

@@

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
%% Tthe amsmath package provides the "align" environment for nicer equation formatting
\usepackage{amsmath}
%% The package tabls helps in having nicer tables with higher spaces
\usepackage{tabls}
%% The package multirow allows merging together multiple cells vertifcally
\usepackage{multirow}
%% The package subcaption is for helping when using subfigures and their captions
\usepackage{subcaption}
%% This package is used for having nicer tables
\usepackage{booktabs}

@@

For both auxiliary and main engines, part of the relevant internal variables are not measured (particularly with relation to the bypass valves) and this required to determine them based on modeling the heat and mass balance of the engine. 
\begin{align}
	\dot{m}_{air,comp} & =  \dot{m}_{air,cyl} + \dot{m}_{air,bp} \label{eq:mb:comp} \\ 
	\dot{m}_{eg,turb} & = \dot{m}_{eg,cyl} + \dot{m}_{air,bp} \label{eq:mb:turb} \\
	\dot{m}_{eg,cyl} & = \dot{m}_{air,cyl} + \dot{m}_{fuel,cyl} \label{eq:mb:cyl} \\
	\dot{m}_{air,comp} \Delta h_{comp} & = \dot{m}_{eg,turb} c_{p,eg} (T_{turb,in} - T_{turb,out}) \eta_{mech} \label{eq:eb:turbocharger} \\
	\dot{m}_{eg,turb} c_{p,eg} (T_{turb,in} - T_0) & = \dot{m}_{air,bp} c_{p,air} (T_{comp,out} - T_0) + \dot{m}_{eg,cyl} c_{p,eg}  (T_{cyl,out} - T_0) \label{eq:eb:bpmerge}
\end{align}
Where equations \ref{eq:mb:comp} to \ref{eq:mb:cyl} represent the mass balances of the bypass split, bypass merge, and cylinder respectively, while equations \ref{eq:eb:turbocharger} and \ref{eq:eb:bpmerge} represent the energy balances of the turbocharger and of the bypass merge, respectively.

The energy balance over the whole engine is presented in Equation \ref{eqn:engineEnergyBalance}.
\begin{equation}
\dot{Q}_{fuel} + \dot{Q}_{air,in} = \dot{W}_{mech} + \dot{Q}_{eg} + \dot{Q}_{cooling}  \label{eqn:engineEnergyBalance} \\
\end{equation}
With: 
\begin{align}
\dot{Q}_{fuel} & =\dot{m}_{fuel} (LHV_{fuel} + c_{p,fuel} (T_{fuel,in} - T_0))\\
\dot{Q}_{air,in} & = \dot{m}_{air} c_{p,air} (T_{air,comp,in} - T_0) \\ 
\dot{Q}_{eg} & = \dot{m}_{eg} c_{p,eg} (T_{eg,TC,out} - T_0) \\
\dot{Q}_{cooling} & = \dot{Q}_{CAC,HT} + \dot{Q}_{CAC,LT} + \dot{Q}_{JWC} + \dot{Q}_{LOC} \label{eq:eb:cooling}
\end{align}

The value of $\dot{Q}_{cooling}$ is determined based on the balance in Equation \ref{eqn:engineEnergyBalance}. The share between the four contributions in Equation \ref{eq:eb:cooling} is calculated based on the data for the heat loss to the HT and LT systems presented in the engines project guides as functions of the engine load. The values are interpolated based on a 2$^nd$ degree polynomial and scaled to respect the energy balance. In absence of more accurate data, it is then assumed that the contributions of $\dot{Q}_{JWC}$ and $\dot{Q}_{LOC}$ are equal for all loads. CHANGE VALUES IN THE TABLE

Values for temperatures, mass flows and energy flows for different engine loads are provided in the Appendix \ref{sec:appendix:engines}, for both main and auxiliary engines.

@@

All values not directly measured in the cooling systems were calculated based on mass and energy balances. The mass flow was determined based on measurements of the pressure in the system and on the performance curves of the cooling pumps.

@@

\subsection{Electric power demand} \label{sec:met:electric}

@@

\subsection{Heat demand} \label{sec:met:heat}

@@

\subsection{Determination of typical operational conditions}

@@

Figures \ref{fig:TseaTairTIME} and \ref{fig:TseaTairDIST} represent the time evolution and the distribution over the year of the ambient air and sea water temperature. The relatively low temperatures that are experienced by the case study ship during its operations rise expectations for a high space heating demand and to a relatively low for summer HVAC electric power demand. On the other hand, the fact that, in summer, air temperatures reach up to 26 degrees Celsius justify the existence of an HVAC unit that can also operate in cooling mode.

@@

Figure \ref{fig:vship_hist} represents the distribution of the ship speed. The ship operates almost for the entire year according to a fix schedule, while there are a couple of periods (particularly during the summer months) when the ship operates at higher speed. In Figure \ref{fig:opMode_pie} it can be also observed that the ship spends a relatively high amount of time in port. These remarks suggest that, in spite of the high installed power of the main engines, the energy demand for propulsion is expected to be relatively low.

Figures \ref{fig:loadME_hist} and \ref{fig:loadME_hist} show the frequency of the load at which each of the engines (main and auxiliary engines, respectively) is operated. In the case of the main engines, it can be observed that they are operated mostly at loads between 30\% and 60\%, despite the optimal load for the engines being located around 85\%. This is a consequence of both the low speed at which the ship is generally operated, and of the fact that the two shaft lines are operated independently, and hence do not allow the use of only one of the four engines at high load.

In the case of the auxiliary engines, a larger difference between how the engines are operated can be observed. AE-3 is generally more often operated, as it is the engine that is run in port with clean fuels. On the other hand, it seems that AE-4 is operated rarely, which might be due to maintenance issues.

@@

The ship energy demand is first subdivided among three main consumer categories: propulsion, electric power, and heat. The evolution of these demands over time during a typical voyage is shown in Figures \ref{fig:Demand_vs_time_W} and \ref{fig:Demand_vs_time_S}, representing a winter and a summer day respectively. It can be seen clearly how, as expected, the heating demand in winter is higher than in summer [2800-4500 kW vs 1100-2900 kW], as a consequence of the reduced need for compartment heating. On the other hand, the electric power demand behaves inversely, ranging around 1900 kW during the reference winter day (peaks are connected to the use of thrusters in port for maneuvering) and around 2300 kW during the reference summer day, where the difference is mostly associated to the demand of the HVAC compressors. Looking at the yearly cumulated demand, nearly 50\% of the total energy demand is related to ship propulsion (see Figure \ref{fig:Pie_EnergyDemand}), while the remaining portion is approximately equally split between electric energy and heat demand.

@@

Within the electric energy demand, the HVAC systems only represent a minor contribution (3\%), as it is only present for a few months during summer. This is not surprising, since it can be observed that (see Figure \ref{fig:TseaTairDIST}) the air is always below 27$^o$C, and rarely above 17$^o$C. Also the thrusters, although their instantaneous power demand is high, are only used for a very short time each day and, hence, their total contribution to the ship electrical energy demand is limited to 1.5\%.

Heat recovery has a large impact on the overall heat demand (see Fig.  \ref{fig:Pie_HeatGeneration}). The the exhaust gas boilers and the heat recovery on the HT-water fulfill almost 75\% of the yearly demand for heating, leaving only the remaining 25\% to be provided by oil-fired auxiliary boilers. The contribution of the HRSG and the HTHR is substantially constant throughout the year (Fig. \ref{fig:TimeSeries_HeatGeneration}), while the auxiliary boilers are used to cover the peaks and the winter increased baseload.

@@

Looking at heating from the demand side, it can be seen that the HVAC pre-heater represents the largest contributor (56\%) to the annual heating demand, followed by the hot water heater (18\%) and by the galley (11\%).In multi-season central HVAC systems the pre-heater is generally used for the main heating contribution during winter, while the re-heater is only used for peak demand, or for adjusting the delivery air temperature during summer, thus explaining the large contribution of the former. The relatively large share of the hot water heater can instead be related to the fact that these systems are used during all seasons.

The full Sankey diagram representation of the energy flows on board is provided in Figure \ref{fig:Sankey}.

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Sankey_diagram_energy_ship_v9}
	\caption{Sankey diagram}
	\label{fig:Sankey}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Grassmann_diagram_v5}
	\caption{Grassmann diagram}
	\label{fig:Grassmann}
\end{figure}

It can be observed that there are large irreversibilities concentrated in some specific parts of the system that show potential for improvement. This is particularly the case of the LT/HT merging valves, where exergy is destroyed in the mixing process. Another substantial source of exergy destruction is the steam heater in the HTHR system, where heat at medium pressure (6 bar) is used to heat up water at 90$^o$C. The analysis of exergy destruction also points out the HVAC reheater as a potential source of improvement, based on the use of relatively high-temperature water for heating up air to around 30$^o$C and on the large energy demand of the component. Other important exergy destruction sources can be located in the engines, as expected, but the improvement of engine processes and technology goes beyond the scope of this work. 
\begin{table}
	\centering
	\begin{tabular}{cc}
		\hline 
		Component name & Contribution to exergy losses \\ 
		\hline 
		LT-HT merge & 13.4\% \\ 
		\hline 
		Sea water cooler & 10.6\% \\ 
		\hline 
		Steam heater & 6.0\% \\ 
		\hline 
		HVAC preheater & 6.0\% \\ 
		\hline 
	\end{tabular} 
	\caption{Major contributors to ship exergy losses. Losses related to combustion are not included in the calculation}
	\label{tab:exergyDestruction}
\end{table}

From the point of view of the exergy losses, it appears that the largest exergy losses are located in the exhaust gas. It should be noted that, even though a large part of this exergy cannot be recovered given the limitations on the exhaust gas outlet temperature to avoid the condensation of sulphuric acid, there is still a significant potential to be harvested if all the available exergy in the exhaust gas was recovered. This potential is further increased by the exergy destroyed in the process of dumping steam when it is produced in excess during summer. The exergy lost in the sea water coolers as low-temperature sea water discharged to the environment is lower, highlighting the fact that the potential for improving the efficiency of the system is located in other parts of the cooling systems.

@@

Add reduction of non-HVAC el demand. Say absorption chillers are useless

@@

\section{Engine modelling, figures and tables}

\begin{table}
	\small
	\centering
	\begin{tabular}{lcrrrr}
		\hline
		Energy flow & type & 30\% & 50\% & 70\% & 90\% \\
		\hline
		Power output & Mech &  1767 & 2946 & 4118 & 5293 \\	
		Exhaust gas (after turbine) & Heat & 1672 & 2566 & 3227 & 3938 \\
		CAC-LT & Heat & 80 & 197 & 353 & 613 \\
		CAC-HT & Heat & 0 & 256  & 470 & 763  \\
		JWC & Heat & 501 & 507 & 549 & 620 \\
		LOC & Heat & 501 & 507 & 549 & 620 \\
		\hline
	\end{tabular}
	\caption{Main engines, energy flows at different engine loads}
	\label{tab:ME_flows}
\end{table}

		Exhaust gas (after turbine) & Heat & 808 & 1144 & 1456 & 1753 \\
		CAC-LT & Heat & 5 & 92 & 139 & 185 \\
		CAC-HT & Heat & 0 & 4 & 87 & 256  \\
		JWC & Heat & 278 & 366 & 436 & 510 \\ 
		LOC & Heat & 278 & 366 & 436 & 510 \\ 
		\hline
	\end{tabular}
	\caption{Auxiliary engines, energy flows at different engine loads}
	\label{tab:AE_flows}
\end{table}

@@

\subsection{Exergy flows}

\begin{table}
	\centering
	\begin{tabular}{clclcrrrrrrrr}
\toprule
\multicolumn{2}{c}{From} & \multicolumn{2}{c}{To}  & Type & Total & Port/Stay & Low Speed Sailing & Maneuvering & High Speed Sailing & Winter & Mid-Season & Summer\\
\midrule
E & Env. & ME & Comp. & Ph & 0.16 & 0.000 & 0.141 & 0.013 & 0.010 & 0.102 & 0.048 & 0.014\\
ME & Comp. & ME & CAC-HT & Ph & 13.64 & 0.004 & 9.932 & 1.148 & 2.555 & 4.976 & 5.626 & 3.037\\
ME & CAC-HT & ME & CAC-LT & Ph & 12.20 & 0.004 & 9.008 & 1.023 & 2.164 & 4.476 & 5.079 & 2.643\\
ME & CAC-LT & ME & Cyl. & Ph & 11.04 & 0.004 & 8.144 & 0.932 & 1.960 & 4.019 & 4.619 & 2.401\\
ME & Turb. & ME & Comp. & W & 20.16 & 0.006 & 15.287 & 1.659 & 3.207 & 7.539 & 8.523 & 4.098\\
ME & Cyl. & ME & Turb. & Ph & 55.91 & 0.037 & 43.951 & 4.839 & 7.085 & 22.177 & 23.408 & 10.327\\
ME & Turb. & E & HRSG & Ph & 15.45 & 0.014 & 12.621 & 1.353 & 1.458 & 6.605 & 6.320 & 2.520\\
ME & Turb. & E & Losses & Q & 0.81 & 0.001 & 0.653 & 0.069 & 0.087 & 0.341 & 0.338 & 0.131\\
ME & Turb. & E & Env. & Ph & 14.04 & 0.014 & 11.256 & 1.285 & 1.489 & 5.694 & 5.941 & 2.409\\
ME & Comp. & ME & BP valve & Ph & 17.44 & 0.004 & 13.179 & 1.425 & 2.831 & 6.557 & 7.323 & 3.559\\
ME & BP valve & ME & Turb. & Ph & 3.80 & 0.001 & 3.246 & 0.277 & 0.275 & 1.581 & 1.697 & 0.522\\
ME & CAC-HT & CS & HT Cool. & Q & 1.16 & 0.000 & 0.924 & 0.125 & 0.392 & 0.501 & 0.547 & 0.394\\
ME & CAC-LT & CS & LT Cool. & Q & 0.59 & 0.000 & 0.864 & 0.091 & 0.203 & 0.456 & 0.460 & 0.242\\
ME & Cyl. & ME & LOC & Q & 4.18 & 0.011 & 3.442 & 0.443 & 0.286 & 1.860 & 1.758 & 0.565\\
ME & Cyl. & ME & JWC & Q & 8.13 & 0.022 & 6.660 & 0.879 & 0.565 & 3.424 & 3.514 & 1.188\\
ME & JWC & CS & HT Cool. & Q & 5.30 & 0.022 & 6.660 & 0.879 & 0.565 & 3.424 & 3.514 & 1.188\\
ME & LOC & CS & LT Cool. & Q & 2.45 & 0.011 & 3.442 & 0.443 & 0.286 & 1.860 & 1.758 & 0.565\\
ME & Cyl. & E & Losses & Q & 0.63 & 0.002 & 0.525 & 0.067 & 0.040 & 0.275 & 0.271 & 0.088\\
ME & HRSG & S & Boiler & Q & 4.63 & 0.008 & 5.622 & 0.628 & 0.498 & 3.015 & 2.677 & 1.064\\
ME & HRSG & E & Env. & Ph & 8.69 & 0.006 & 6.999 & 0.725 & 0.961 & 3.590 & 3.643 & 1.456\\
ME & Cyl. & P & Prop. shaft & W & 107.39 & 0.141 & 85.158 & 10.141 & 11.947 & 42.238 & 45.916 & 19.233\\
ME & Fuel tank & ME & Cyl. & Ch & 266.02 & 0.382 & 212.237 & 25.450 & 27.949 & 105.146 & 114.197 & 46.675\\
ME & Fuel tank & ME & Cyl. & Q & 0.15 & 0.000 & 0.125 & 0.014 & 0.014 & 0.068 & 0.063 & 0.022\\
\midrule
E & Env. & AE & Comp. & Ph & 0.01 & 0.002 & 0.003 & 0.001 & 0.000 & 0.003 & 0.001 & 0.001\\
AE & Comp. & AE & CAC-HT & Ph & 7.91 & 2.960 & 4.008 & 0.659 & 0.288 & 3.392 & 3.091 & 1.432\\
AE & CAC-HT & AE & CAC-LT & Ph & 7.65 & 2.835 & 3.906 & 0.644 & 0.269 & 3.302 & 3.017 & 1.335\\
AE & CAC-LT & AE & Cyl. & Ph & 7.09 & 2.589 & 3.650 & 0.606 & 0.248 & 3.066 & 2.802 & 1.227\\
AE & Turb. & AE & Comp. & W & 9.54 & 3.504 & 4.853 & 0.841 & 0.338 & 4.087 & 3.762 & 1.687\\
AE & Cyl. & AE & Turb. & Ph & 36.26 & 11.776 & 19.815 & 3.592 & 1.079 & 15.705 & 14.961 & 5.597\\
AE & Turb. & E & HRSG & Ph & 21.04 & 6.378 & 11.936 & 2.157 & 0.571 & 9.166 & 8.866 & 3.011\\
AE & Turb. & E & Losses & Q & 0.46 & 0.132 & 0.259 & 0.060 & 0.012 & 0.209 & 0.194 & 0.060\\
AE & Comp. & AE & BP valve & Ph & 7.91 & 2.960 & 4.008 & 0.659 & 0.288 & 3.392 & 3.091 & 1.432\\
AE & BP valve & AE & Turb. & Ph & 0.00 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
AE & CAC-HT & CS & HT Cool. & Q & 0.24 & 0.125 & 0.102 & 0.015 & 0.018 & 0.090 & 0.074 & 0.097\\
AE & CAC-LT & CS & LT Cool. & Q & 0.36 & 0.245 & 0.256 & 0.037 & 0.021 & 0.236 & 0.215 & 0.108\\
AE & Cyl. & AE & LOC & Q & 3.14 & 0.962 & 1.757 & 0.344 & 0.075 & 1.476 & 1.275 & 0.388\\
AE & Cyl. & AE & JWC & Q & 5.84 & 1.772 & 3.270 & 0.656 & 0.144 & 2.608 & 2.451 & 0.783\\
AE & JWC & CS & HT Cool. & Q & 3.90 & 1.772 & 3.270 & 0.656 & 0.144 & 2.608 & 2.451 & 0.783\\
AE & LOC & CS & LT Cool. & Q & 2.18 & 0.962 & 1.757 & 0.344 & 0.075 & 1.476 & 1.275 & 0.388\\
AE & Cyl. & E & Losses & Q & 0.37 & 0.096 & 0.217 & 0.047 & 0.008 & 0.166 & 0.159 & 0.044\\
AE & HRSG & S & Boiler & Q & 6.32 & 2.869 & 5.504 & 1.011 & 0.237 & 4.309 & 3.901 & 1.412\\
AE & HRSG & E & Env. & Ph & 11.42 & 3.509 & 6.432 & 1.145 & 0.334 & 4.857 & 4.965 & 1.599\\
AE & Cyl. & EL & SB & W & 62.02 & 20.781 & 34.328 & 6.249 & 1.851 & 26.971 & 26.344 & 9.894\\
AE & Cyl. & E & AG losses & Q & 0.85 & 0.228 & 0.499 & 0.105 & 0.020 & 0.384 & 0.363 & 0.104\\
AE & Fuel tank & AE & Cyl. & Ch & 172.09 & 54.452 & 94.876 & 17.916 & 4.849 & 73.199 & 72.744 & 26.150\\
AE & Fuel tank & AE & Cyl. & Q & 0.08 & 0.019 & 0.054 & 0.009 & 0.003 & 0.041 & 0.033 & 0.010\\
\midrule
CS & HT Cool. & CS & LT Cool. & Q & 7.36 & 1.46 & 8.63 & 1.36 & 0.97 & 5.10 & 5.25 & 2.08\\
CS & HT Cool. & S & HRHT & Q & 3.24 & 0.46 & 2.33 & 0.31 & 0.14 & 1.53 & 1.34 & 0.38\\
S & Boiler & S & HRHT & Q & 10.87 & 4.94 & 5.09 & 0.75 & 0.09 & 6.51 & 3.82 & 0.53\\
S & Aux Boiler & S & Boiler & Ph & 5.71 & 4.66 & 0.90 & 0.17 & -0.03 & 3.77 & 1.85 & 0.10\\
S & Aux Boiler & E & Env. & Ph & 1.51 & 1.04 & 0.38 & 0.08 & 0.00 & 0.99 & 0.50 & 0.03\\
S & Fuel tank & S & Aux Boiler & Ch & 20.12 & 14.37 & 4.73 & 1.02 & 0.01 & 12.99 & 6.76 & 0.37\\
S & HRHT & D & HVAC-PH & Q & 7.43 & 1.22 & 1.89 & 0.25 & 0.05 & 2.29 & 1.11 & 0.00\\
S & HRHT & D & HVAC-RH & Q & 0.33 & 0.09 & 0.13 & 0.03 & 0.03 & 0.00 & 0.00 & 0.28\\
S & HRHT & D & HWH  & Q & 2.27 & 0.64 & 1.09 & 0.17 & 0.05 & 0.84 & 0.81 & 0.31\\
S & Boiler & D & MSH & Q & 0.68 & 0.06 & 0.10 & 0.01 & 0.00 & 0.09 & 0.07 & 0.02\\
S & Boiler & D & HFO TH & Q & 0.66 & 0.13 & 0.20 & 0.03 & 0.01 & 0.16 & 0.16 & 0.04\\
S & Boiler & D & HFO H & Q & 0.44 & 0.04 & 0.21 & 0.03 & 0.02 & 0.13 & 0.12 & 0.04\\
S & Boiler & D & TH & Q & 0.51 & 0.08 & 0.12 & 0.02 & 0.01 & 0.11 & 0.10 & 0.03\\
S & Boiler & D & G & Q & 2.45 & 0.44 & 0.98 & 0.14 & 0.04 & 0.71 & 0.69 & 0.19\\
S & Boiler & D & OT & Q & 0.34 & 0.08 & 0.12 & 0.02 & 0.01 & 0.11 & 0.10 & 0.03\\
EL & SB & EL & Thrusters & W & 0.94 & 0.00 & 0.00 & 0.94 & 0.00 & 0.36 & 0.43 & 0.15\\
EL & SB & EL & HVAC & W & 1.79 & 0.59 & 0.85 & 0.18 & 0.18 & 0.00 & 0.00 & 1.79\\
EL & SB & EL & Other el. Dem. & W & 59.29 & 19.99 & 32.66 & 4.99 & 1.64 & 26.06 & 25.45 & 7.78\\
P & Prop. shaft & P & Prop. & W & 104.19 & 0.14 & 82.62 & 9.84 & 11.59 & 40.98 & 44.55 & 18.66\\
P & Prop. shaft & E & Losses & Q & 3.20 & 0.00 & 2.54 & 0.30 & 0.36 & 1.26 & 1.37 & 0.57\\
S & Boiler & E & Dumped steam & Q & 0.81 & 0.00 & 0.43 & 0.13 & 0.25 & 0.05 & 0.20 & 0.55\\
\midrule
& HVAC-PH & D & Dem. & Q & 3.41 & 1.22 & 1.89 & 0.25 & 0.05 & 2.29 & 1.11 & 0.00\\
& HVAC-RH & D & Dem. & Q & 0.28 & 0.09 & 0.13 & 0.03 & 0.03 & 0.00 & 0.00 & 0.28\\
& HWH  & D & Dem. & Q & 1.96 & 0.64 & 1.09 & 0.17 & 0.05 & 0.84 & 0.81 & 0.31\\
& MSH & D & Dem. & Q & 0.18 & 0.06 & 0.10 & 0.01 & 0.00 & 0.09 & 0.07 & 0.02\\
& HFO TH & D & Dem. & Q & 0.37 & 0.13 & 0.20 & 0.03 & 0.01 & 0.16 & 0.16 & 0.04\\
& HFO H & D & Dem. & Q & 0.29 & 0.04 & 0.21 & 0.03 & 0.02 & 0.13 & 0.12 & 0.04\\
& TH & D & Dem. & Q & 0.23 & 0.08 & 0.12 & 0.02 & 0.01 & 0.11 & 0.10 & 0.03\\
& G & D & Dem. & Q & 1.59 & 0.44 & 0.98 & 0.14 & 0.04 & 0.71 & 0.69 & 0.19\\
& OT & D & Dem. & Q & 0.15 & 0.05 & 0.08 & 0.01 & 0.00 & 0.07 & 0.07 & 0.02\\
\bottomrule
	\end{tabular}
\end{table}
